On the minimum leaf conductance g~0~

### 2017-03-30 manuscript.Rmd
more references

@@

Though the role and potential for estimation using Eq. 1 is clear, it is not clear whether and how g~0~ compares to other estimates of g~s~ when photosynthesis is zero. It is sometimes assumed that g~0~ must equal g~s~ at night, simply since no photosynthesis occurs at night [@lombardozzi2016; @barnard2013]. Other studies assume that g~0~ equals a 'cuticular conductance` [@manzoni2011; @egea2011], but it has yet to be determined how various minimum conductance estimates compare.

@@

similarly at high T. @kala2016 @urban 
drake in prep
duursma2014

>>>>

g~0~ usually ignored, for example in recent review of stomatal conductance models [@damour2010]

@@

Though the role and potential for estimation using Eq. 1 is clear, it is not clear whether and how g~0~ compares to other estimates of g~s~ when photosynthesis is zero. It is sometimes assumed that g~0~ must equal g~s~ at night, simply since no photosynthesis occurs at night [@lombardozzi2016; @barnard2013; @uddling2005]. Other studies assume that g~0~ equals a 'cuticular conductance` [@baldocchi1997; @manzoni2011; @egea2011], but it has yet to be determined how various minimum conductance estimates compare.

@@

similarly at high T, which is important [@kala2016]

The assumption of Eq. 1 is that g~s~ goes to g~0~ both at low light and very high temperature, when A <-- 0 [@duursma2014]. Some studies however show that stomata don't shut at high T [@urban2017].
Another thing is that the effect is actually larger than g~0~ because this additional conductance allows slightly more stomatal opening (because photosynthesis occurs more because of higher g~s~).
